Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-08 src/article.tex
Revise abstract

  \paragraph*{Background:} Assembly of short-read sequencing data can result in
  a fragmented non-contiguous series of genomic sequences. Therefore a common
  step in a genome project is to join neighbouring sequence regions together
  and fill gaps in the assembly using additional sequence. This scaffolding
  step, however, is non-trivial and requires manually editing large blocks of
  nucleotide sequence. Joining sequence contigs together also hides the source
  of each region in the final genome sequence. Taken together, these
  considerations may make reproducing or editing an existing genome build
  difficult.

@@

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent sequences using a relatively simple format to write
  and edit scaffold file syntax. This syntax further allows  unknown regions to
  be defined, and inserts to be added to the scaffold to fill gaps. Defining
  the genome construction in a file makes the scaffolding process reproducible
  and easier to edit and compare than FASTA nucleotide sequence.

>>>>

  \paragraph*{Background:} Assembly of short-read sequencing data can result in
  a fragmented non-contiguous series of genomic sequences. Therefore a common
  step in a genome project is to join neighbouring sequence regions together
  and fill gaps in the assembly using additional sequences. This scaffolding
  step, however, is non-trivial and requires manually editing large blocks of
  nucleotide sequence. Joining these sequences together also hides the source
  of each region in the final genome sequence. Taken together, these
  considerations may make reproducing or editing an existing genome build
  difficult.

@@

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent sequences using a relatively simple syntax to
  define the scaffold. This syntax further allows  unknown regions to be
  defined, and add inserts to fill gaps in the scaffold. Defining the genome
  construction in a file makes the scaffolding process reproducible and easier
  to edit compared with FASTA nucleotide sequence.
